Damage localization based on vibrations

### 2016-12-06 rapport/paper.tex
slides

Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (4 in total), in function of frequencies. We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak. Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system. It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{images/FRF_freq.png}
  \caption{FRF of one sensor (4 in total), in function of frequencies}
  \label{frf_freq}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{images/curve_damage.png}
  \caption{FRF values for 10 sensors, at a fixed frequency}
  \label{damage}
\end{figure}

>>>>

Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (ten in total), against frequencies. We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak. Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system. It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{images/persensor1.png}
  \caption{FRF of one sensor (ten in total), against frequencies}
  \label{frf_freq}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{images/damaged4.png}
  \caption{FRF values for 10 sensors, at a fixed frequency}
  \label{damage}
\end{figure}

### 2016-12-06 slides/slides.tex
slides

\documentclass{beamer}
  \usepackage[utf8]{inputenc}
  \usepackage{graphicx}
  \usepackage{array}
  \usepackage{url}
  \usetheme{Warsaw}

@@

\begin{center}
\begin{itemize}[<+->]
\item Detection: Is the structure damaged or not?
\vspace{1\baselineskip}
\item Localization: Where is the damaged area located?
\vspace{1\baselineskip}
\item Quantification: What is the extent of damage?
\vspace{1\baselineskip}
\item Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

@@

\begin{frame}{transition}
\end{frame}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{FRF calcul}
\begin{frame}{FRF calcul}
\end{frame}

\subsection{Interpolation}
\begin{frame}{Interpolation}
Cubic polynomial spline interpolation:

\begin{center}
\includegraphics[width=5cm]{images/interpolation.png}
\end{center}

For each sensor $z_l$ at the frequency $f_i$:
\begin{center}
$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
\end{center}

@@

@@

\subsection{FRF and Interpolation}
\begin{frame}{FRF and Interpolation}
\end{frame}

\subsection{Results}
\begin{frame}{Results 1/3}
\begin{center}
\includegraphics[width=5cm]{images/FRF_freq.png}

FRF for one sensor in function of frequencies
\end{center}
\end{frame}

\begin{frame}{Results 2/3}
\begin{center}
\includegraphics[width=5cm]{images/curve_damage.png}

For a fixed frequency, the FRF value for each sensor
\end{center}

@@

\begin{frame}{Results 3/3}
\end{frame}

@@

\begin{frame}{Conclusion}
\end{frame}

>>>>

\documentclass{beamer}
  \usepackage[utf8]{inputenc}
  \usepackage{graphicx}
  \usepackage{array}
  \usepackage{url}
  \usepackage{color}
  \usetheme{Warsaw}

@@

\begin{center}
\begin{itemize}
\item<1-> Detection: Is the structure damaged or not?
\vspace{1\baselineskip}
\item<2-|alert@5> Localization: Where is the damaged area located?
\vspace{1\baselineskip}
\item<3-> Quantification: What is the extent of damage?
\vspace{1\baselineskip}
\item<4-> Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

@@

\begin{center}
Data driven method
\end{center}

\pause

\pause

\subsection{FRF calcul}
\begin{frame}{FRF calcul}
\begin{exampleblock}{Frequency Response Function}
\begin{center}
$H = \frac{Y}{F}$
\end{center}
$F$: input

$Y$: output
\end{exampleblock}

\pause

Fourier transform:
$
F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N},
Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
$

\begin{block}{Estimator}
\begin{center}
$H_1(n) = \frac{Y_n}{F_n}$
\end{center}
\end{block}

\subsection{Interpolation}
\begin{frame}{Interpolation}
\underline{Cubic polynomial spline interpolation:}
\begin{itemize}
\item piecewise continuous curve, passing through each of the values
\item continuous through to the second derivative
\end{itemize}

\begin{center}
\includegraphics[width=5cm]{images/interpolation_spline.png}
\end{center}

\begin{center}
\includegraphics[width=6cm]{images/interpolation.png}
\end{center}

For each sensor $z_l$ at the frequency $f_i$:
$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$

\pause

\pause

@@

@@

@@

\pause

@@

\subsection{Results}
\begin{frame}{Results 1/4}
\begin{center}
\includegraphics[height=4cm]{images/persensor1.png}
\hfill
\includegraphics[height=4cm]{images/persensor2.png}

FRF for one sensor against frequencies
\end{center}
\end{frame}

\begin{frame}{Results 2/4}
\begin{center}
\includegraphics[height=4cm]{images/damaged4.png}
\hfill
\includegraphics[height=4cm]{images/damaged_curve.png}

For a fixed frequency, the FRF value for each sensor

Damage between sensors 4 and 5
\end{center}

@@

\begin{frame}{Results 3/4}
\begin{center}
\includegraphics[height=4cm]{images/damaged2.png}
\hfill
\includegraphics[height=4cm]{images/damaged3.png}

For a fixed frequency, the FRF value for each sensor

Damage between sensors 4 and 5
\end{center}
\end{frame}

\begin{frame}{Results 4/4}
\begin{center}
\includegraphics[height=4cm]{images/globalerror.png}

Global error

Damage between sensors 4 and 5
\end{center}

@@

\begin{frame}{Conclusion}
\underline{What we did:}
\begin{itemize}
\item State of the art
\item Implementation of the FRF interpolation method with a simulation
\end{itemize}

\underline{What we will do:}
\begin{itemize}
\item Development of a statistical extension of this method
\end{itemize}
